---
title: "Prediction using Unsupervised ML"
author: "Soham Bagchi"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

### ABOUT THE DATASET

The Iris flower data set or Fisher's Iris data set is a multivariate data set introduced by the British statistician, eugenicist, and biologist Ronald Fisher in his 1936 paper .

```{r}
iris<-read.csv(file.choose())
iris<-iris[2:6]
```
### Exploring the data
```{r}
str(iris)
summary(iris)
```
Preparing the dataset to apply clustering
```{r}
iris.s<-iris
iris.s$Species<-NULL

```
### Using the elbow method to find the optimal number of clusters
```{r}
set.seed(6)
wcss<-vector()
for (i in 1:10)
{
  wcss[i]<-sum(kmeans(iris.s,i)$withinss)
}
plot(1:10,wcss,type="b",main=paste("Elbow method to find the optimal number of clusters"),xlab="Number of clusters",ylab="Within cluster sum square")

``` 
  
  It is called 'The elbow method' as from the above graph,we get the optimum clusters  where the elbow occurs.So we see that the number of clusters as  '3'.

```{r}
set.seed(56)
result<-kmeans(iris.s,3,iter.max = 300,nstar=10)
result
```
### Confusion matrix
Lets compare the clusters with the species
```{r}

table(iris$Species,result$cluster)
plot(table(iris$Species, result$cluster),
      main="Confusion Matrix for Clustering",
      xlab="Species", ylab="Cluster")
```

### Visualizing the clusters

```{r}
library(ggplot2)
result$cluster<-as.factor(result$cluster)
center<-data.frame(result$centers)

ggplot(iris.s)+geom_point(aes(x=PetalLengthCm,y=PetalWidthCm,color = result$cluster))+geom_point(data=center,aes(x=PetalLengthCm,y=PetalWidthCm),shape=5,color="black",size=4)+labs(x="Petal Length(in cm)",y="Petal Width(in cm)")+ggtitle("Visualizing the clusters",subtitle = "on petal length and petal width")

ggplot(iris.s)+geom_point(aes(x=SepalLengthCm,y=SepalWidthCm,color = result$cluster))+geom_point(data=center,aes(x=SepalLengthCm,y=SepalWidthCm),shape=5,color="black",size=4)+labs(x="Sepal Length(in cm)",y="Sepal Width(in cm)")+ggtitle("Visualizing the clusters",subtitle = "on sepal length and sepal width")

```



